\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{A Radial Time Projection Chamber for $\alpha$ detection in CLAS at JLab}

### 2017-05-01 eg6-letters/NIM/EG6_RTPC_NIM.tex
update the nim paper with the proper dedx vs p/q distributions

Measurement of the Deeply Virtual Compton Scattering (DVCS) process
($eH \rightarrow e' H' \gamma$, where $H$ is a hadron) necessitates an upgrade
of this setup.  With a 6 GeV electron beam, the majority of DVCS photons are produced
at very forward angles, where the acceptance of the EC is poor. To extend the detection range,
an inner calorimeter (IC) was built for the E01-113 experiment in 2005.
The IC is constructed from 424 lead-tungstate (PbWO$_{4}$) crystals, covering polar 
angles between 5$^{\circ}$ and 15$^{\circ}$. Each crystal is 16 cm long, corresponding
to 17 radiation lengths. The achieved energy resolution is around 3 to 4$\%$ for photon
energies between 2 GeV and 5 GeV, with an angular resolution between 3 and 5 mrad 
\cite{Hyon-suk}. To protect this detector from the large flux of low energy M{\o}ller 
electrons, a 5~T solenoid was placed around the target to shield the IC. 
In addition, the recoil nuclei of the coherent DVCS on helium was detected 
using a RTPC developed to track low energy nuclear fragments. The solenoid field
serving as the analyzing magnet for the particle tracking in the RTPC. This 
setup was used during a three months experimental run
in 2009 with a longitudinally polarized electron beam of 6.064 GeV incident 
on a gaseous $^{4}$He target.
{\bf \color{red} Add beam current or luminosity.}

@@

The GEM technology has been chosen for this RTPC for its flexibility, 
allowing a curved amplification surface. Also, GEMs are known to rarely create 
sparks{\bf \color{red} Need reference.}, which is important when trying to 
detect highly ionizing slow nuclei that deposit large amount of energy. The 
GEMs for this RTPC are made from a Kapton insulator layer 
{\bf \color{red} Thickness?} sandwiched between two 5 $\mu$m copper
layers. The mesh of each GEM layer is chemically etched with 50$\mu$m diameter
holes with double-conical shapes as illustrated in figure~\ref{fig:GEMs}. A
potential difference of 400 V {\bf \color{red} To be checked and set as above.} 
is applied between the two copper layers of the
GEM, creating a very strong electric field in each hole leading to high ionization 
and therefore amplification of the incoming electrons. A 
potential of 150 V {\bf \color{red} To be checked.} 
is set between the GEMs to push the electrons toward the next GEM and eventually 
the readout pads. The gain of each GEM layer is of order 100, making a total gain 
of about $10^{6}$. {\bf \color{red} We should quote a realistic overall gain or nothing.}\\

@@

\begin{figure}[tb]
   \includegraphics[scale=0.26]{fig/dedx_p_exp_1st.png}
   \caption{$\small{\frac{dE}{dX}}$ vs. $p$ distribution for the left half of the 
      RTPC (left) and for the right half (right). Here, $\small{\frac{dE}{dX}}$ 
   is calculated using the gains of the first method.  The lines are 
theoretical expectations from Bethe-Bloch formula for $^4$He, $^3$He, $^3$H and 
$^2$H (d).{\bf \color{red} Mohammad: Did you multiply p/c by 2 in the figure? If no 
change the caption, if yes check remove the single charge nuclei from the figure 
because there is a consistency issue.}}
\label{fig:dedx_p_exp_1st}
\end{figure}

@@

\begin{figure}[tb]
\includegraphics[scale=0.350]{fig/EVENT_adc_tdc.png}
\caption{Simulated (upper) and experimental (lower) ADCs and TDCs distributions 
of a track. The colors indicate the pads, same color in top and bottom indicate 
that they are the same pad.}
\label{fig:EVENT_adc_tdc}
\end{figure}

\begin{figure}[tb]
\centering
\includegraphics[scale=0.26]{fig/dedx_p_exp_2nd.png}
\caption{$\small{\frac{dE}{dX}}$ vs. $p$ distribution for the left half of the 
   RTPC (left) and for the right half (right). Here, $\small{\frac{dE}{dX}}$ is 
   calculated using the gains of the second method.  The lines are theoretical 
   expectations from Bethe-Bloch formula for $^4$He, $^3$He, $^3$H and $^2$H 
(d).{\bf \color{red} Mohammad: Did you multiply p/c by 2 in the figure? If no 
change the caption, if yes check remove the single charge nuclei from the figure 
because there is a consistency issue.}}
\label{fig:dedx_p_exp_2nd}
\end{figure}

@@

>>>>

Measurement of the Deeply Virtual Compton Scattering (DVCS) process
($eH \rightarrow e' H' \gamma$, where $H$ is a hadron) necessitates an upgrade
of this setup.  With a 6 GeV electron beam, the majority of DVCS photons are produced
at very forward angles, where the acceptance of the EC is poor. To extend the detection range,
an inner calorimeter (IC) was built for the E01-113 experiment in 2005.
The IC is constructed from 424 lead-tungstate (PbWO$_{4}$) crystals, covering polar 
angles between 5$^{\circ}$ and 15$^{\circ}$. Each crystal is 16 cm long, corresponding
to 17 radiation lengths. The achieved energy resolution is around 3 to 4$\%$ for photon
energies between 2 GeV and 5 GeV, with an angular resolution between 3 and 5 mrad 
\cite{Hyon-suk}. To protect this detector from the large flux of low energy M{\o}ller 
electrons, a 5~T solenoid was placed around the target to shield the IC. 
In addition, the recoil nuclei of the coherent DVCS on helium was detected 
using a RTPC developed to track low energy nuclear fragments. The solenoid field
serving as the analyzing magnet for the particle tracking in the RTPC. This 
setup was used during a three months experimental run
in 2009 with a longitudinally polarized electron beam of {\color{blue} 130 nA 
and energy of 6.064 GeV} incident on a gaseous $^{4}$He target.
{\bf \color{red} Add beam current or luminosity.}

@@

The GEM technology has been chosen for this RTPC for its flexibility, 
allowing a curved amplification surface. Also, GEMs are known to rarely create 
sparks{\color{blue} \cite{GEM_ref}}, which is important when trying to detect 
highly ionizing slow nuclei that deposit large amount of energy. The GEMs for 
this RTPC are made from a Kapton insulator layer, {\color{blue}50~$\mu$m 
thick}, sandwiched between two 5~$\mu$m copper layers. The mesh of each GEM 
layer is chemically etched with 50~$\mu$m diameter holes with double-conical 
shapes as illustrated in figure~\ref{fig:GEMs}. A potential difference of 400 V 
{\bf \color{red} To be checked and set as above.} is applied between the two 
copper layers of the GEM, creating a very strong electric field in each hole 
leading to high ionization and therefore amplification of the incoming 
electrons. A potential of 150 V {\bf \color{red} To be checked.} is set between 
the GEMs to push the electrons toward the next GEM and eventually the readout 
pads. The gain of each GEM layer is of order 100, making a total gain of about 
$10^{6}$.  {\bf \color{red} We should quote a realistic overall gain or 
nothing.}\\

@@

\begin{figure}[tb]
   \centering
   \includegraphics[scale=0.45]{fig/f_dedx_p_exp_1st.pdf}
   \caption{$\small{\frac{dE}{dX}}$ vs. $p/q$ distribution for the left half of 
      the RTPC (left) and for the right half (right). Here, 
      $\small{\frac{dE}{dX}}$ is calculated using the gains of the first 
      method.  The lines are theoretical expectations from Bethe-Bloch formula 
   for $^4$He, $^3$He, $^3$H and $^2$H (d).}
\label{fig:dedx_p_exp_1st}
\end{figure}

@@

\begin{figure}[tb]
   \centering
\includegraphics[scale=0.350]{fig/EVENT_adc_tdc.png}
\caption{Simulated (upper) and experimental (lower) ADCs and TDCs distributions 
of a track. The colors indicate the pads, same color in top and bottom indicate 
that they are the same pad.}
\label{fig:EVENT_adc_tdc}
\end{figure}

\begin{figure}[tb]
\centering
\includegraphics[scale=0.45]{fig/f_dedx_p_exp_2nd.pdf}
\caption{$\small{\frac{dE}{dX}}$ vs. $p/q$ distribution for the left half of 
   the RTPC (left) and for the right half (right). Here, 
   $\small{\frac{dE}{dX}}$ is calculated using the gains of the second method.  
   The lines are theoretical expectations from Bethe-Bloch formula for $^4$He, 
$^3$He, $^3$H and $^2$H (d).}
\label{fig:dedx_p_exp_2nd}
\end{figure}

@@

\bibitem{GEM_ref}
   J. Beringer et al. (Particle Data Group), Particle detectors at 
   accelerators, Phys. Rev. D 86, 010001, pages: 339-368, 2012.
